The \dealii{} Library, Version 9.0

### 2018-04-12 9.0/paper.tex
Add more names to pdfauthor

\hypersetup{
  pdfauthor={
    Giovanni Alzetta,
    Daniel Arndt,
    Vishal Boddu,
    Benjamin Brands,
    Denis Davydov,
    Rene Gassm\"{o}ller,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler
    Matthias Maier,
    David Wells
  },
  pdftitle={The deal.II Library, Version 9.0, 2018},
}

>>>>

\hypersetup{
  pdfauthor={
    Giovanni Alzetta,
    Daniel Arndt,
    Wolfgang Bangerth,
    Vishal Boddu,
    Benjamin Brands,
    Denis Davydov,
    Rene Gassm\"{o}ller,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler
    Matthias Maier,
    Jean-Paul Pelteret,
    Bruno Turcksin,
    David Wells
  },
  pdftitle={The deal.II Library, Version 9.0, 2018},
}
